### 2025-05-07 project1/nsSurvey.tex
final draft

This paper presents a survey study of some popular nested simulation procedures that have both asymptotic convergence analysis and finite-sample performance evaluation.
Many procedures have been proposed in the literature, but they are not directly comparable because they use \textcolor{red}{\sout{different error metrics,}} different assumptions and different numerical examples in their studies.
Within a common analytical framework, we first summarize and compare the asymptotic convergence rates of these procedures.
Their asymptotic convergence results are closely examined for their assumptions that guarantee the convergence.
\textcolor{red}{\sout{Furthermore, the existing literature has chosen different performance metrics to evaluate the asymptotic convergence of nested simulation procedures.
In this chapter, we discuss the asymptotic convergence in terms of \gls{mse} of the estimator, and we provide a comprehensive comparison of their convergence rates and critical assumptions.
We also discuss the connection between the \gls{mse} and the absolute error of the estimator in the context of nested simulation procedures.}}

@@

The regression-based nested simulation procedure has the least stringent smoothness assumption.
In general, a more complex metamodel requires a higher-order smoothness for $h$ for its convergence analysis.
Despite being more advanced than kernel smoothing, the \gls{krr}-based procedure requires a less stringent smoothness assumption on $h$.
At first sight, it is counterintuitive that a more complex metamodel requires a less stringent smoothness assumption.
This phenomenon is due to the fact that the convergence analysis for the \gls{krr}-based nested simulation procedure is shown in terms of \textcolor{red}{\gls{ae}, a different error metric than \gls{mse}.}
\textcolor{red}{In the appendix,} Section~\ref{appendix:connection-mse-absolute-error} includes a discussion of the connection between the \gls{mse} and the \gls{ae} of the estimator in the context of nested simulation procedures.
In Table~\ref{tab1:smoothness}, the standard nested simulation procedure is the only procedure without an asymptotic convergence analysis for smooth $h$.
Section~\ref{sec1:sns} fills this gap by providing the asymptotic convergence analysis for the standard nested simulation procedure in terms of \gls{mse}.

@@

The \gls{mlmc} method is a variance reduction technique that uses a hierarchy of approximations to the quantity of interest, and it uses the difference between the approximations to reduce the variance of the estimator.
The \gls{mlmc} method is particularly useful when the quantity of interest is expensive to evaluate, and the standard \gls{mc} estimator has a high variance.
\textcolor{red}{For the nested expectation form $\rho = \mathbb{E}[h(L)]$, the \gls{mlmc} method selects an approximation level $L$ with sufficient accuracy, and it uses the difference between the approximations to reduce the variance of the estimator.}
\textcolor{red}{\sout{The \gls{mlmc} method estimates $\rho$ with an \gls{mlmc} estimator:}}

@@

\begin{itemize}
    \item   Regression:
            $$\hat{L}^{\text{REG}}_{M, N}(X) = \Phi(X) \hat{\beta},$$
            where $\Phi$ is a chosen basis, and $\hat{\beta}$ is estimated from the training samples.
            In~\cite{broadie2015risk}, the convergence analysis is performed on the expectation (Equation~\eqref{eq1:sl-E}) and for smooth and Lipschitz continuous $h$. 
    \item   Kernel smoothing:
            $$\hat{L}^{\text{KS}}_{M, N}(X) = \frac{\sum_{i=1}^M \hat{L}_{N, i} K_w(X - X_i)}{\sum_{i=1}^M K_w(X - X_i)}, $$
            where $K_w$ is a kernel function with bandwidth $w$.
            ~\cite{nadaraya1964estimating} and ~\cite{watson1964smooth} originally proposed this kernel smoothing method for a non-parametric regression, and it is widely known in the literature as a Nadaraya-Watson kernel regression.
            ~\cite{hong2017kernel} provides convergence analysis for metamodel predictions of the training samples (Equation~\eqref{eq1:sl-train}), and the convergence analysis is provided for smooth, hockey-stick, and indicator $h$.

@@

\textcolor{red}{Theoretical properties of different metamodels lead to different convergence results.}
More specifically, the \gls{krr}-based nested simulation~\citep{wang2022smooth} provides a convergence analysis in terms of \gls{ae}.
\begin{align}\label{eq1:ae}
    & \min_{M, N}  & \text{AE}(\hat{\rho}^{\text{SL}}_{M, N}) = \mathbb{E} \left[ \left| \hat{\rho}^{\text{KRR}}_{M, N} - \rho \right| \right] \nonumber \\
    & \text{subject to} & M \cdot N = \Gamma
\end{align}
Section~\ref{appendix:connection-mse-absolute-error} draws the connection between the \gls{mse} and the \gls{ae} of the estimator in the context of nested simulation procedures.

@@

\section{Asymptotic Analysis}\label{sec1:asymptotic-convergence}
In the first part of this section, we summarize the existing asymptotic convergence results of the nested simulation procedures in the literature, and we compare their critical assumptions that guarantee the convergence.
The remainder of this section aims to fill the gap in the literature by offering the following steps:
\begin{itemize}
    \item provide the asymptotic convergence results for the standard nested simulation procedure, \textcolor{red}{and}
    \item \textcolor{red}{\sout{show the connections between the convergence in \gls{mse} and the convergence in probabilistic order for \gls{ae} in the context of nested simulation procedures, and}}
    \item illustrate the asymptotic rate of convergence of a \gls{knn}-based nested simulation procedure.
\end{itemize}

@@

In~\cite{wang2022smooth}, the authors of the \gls{krr}-based nested simulation procedures claim to have bridged the gap between the cubic and square root convergence rates of nested simulation procedures. However, they analyze convergence in probabilistic order, and it is only applicable in terms of \gls{ae}. 
\textcolor{red}{In Section~\ref{appendix:connection-mse-absolute-error}, we illustrate the connection between the convergence in \gls{mse} and the convergence in \gls{ae}.}

@@

\textcolor{red}{In Equation~\eqref{eq1:mse-sns}, the first inequality follows from Cauchy-Schwarz inequality.
One way to express the Cauchy-Schwarz inequality is 
$(x_1y_1 + x_2y_2)^2 \leq (x_1^2 + x_2^2)(y_1^2 + y_2^2)$.
Let $\mathbf{x} = (x_1, x_2)$ and $\mathbf{y} = (y_1, y_2)$.
The Cauchy-Schwarz inequality can be written as}
\begin{equation*}
    \langle \mathbf{x}, \mathbf{y} \rangle^2  = \left( \Vert \mathbf{x} \Vert \cdot \Vert \mathbf{y} \Vert \cdot \cos a \right)^2 \leq \Vert \mathbf{x} \Vert^2 \cdot \Vert \mathbf{y} \Vert^2.
\end{equation*}
\textcolor{red}{By setting $x_1 = \rho_{M,N}- \rho_M$, $x_2 = \rho_M - \rho$, $y_1 = y_2 = 1$, we have }
\begin{align*}
    \left( \rho_{M,N} - \rho_M + \rho_M - \rho \right)^2 
    & \leq \left( (\rho_{M,N} - \rho_M)^2 + (\rho_M - \rho)^2 \right) \left( 1^2 + 1^2 \right) \\
    & = 2 \left( (\rho_{M,N} - \rho_M)^2 + (\rho_M - \rho)^2 \right) \\
    & = 2  (\rho_{M,N} - \rho_M)^2 + 2 (\rho_M - \rho)^2.
\end{align*}
The last equality follows from Assumption~\ref{as1:sns}.
The analysis of the first term is different for smooth and Lipschitz continuous $h$. 
We will analyze them separately below.

@@

\begin{align}\label{eq1:taylor-sns}
    & \mathbb{E} \left[  \left( \frac{1}{M} \sum_{i=1}^M h\left( \hat{L}_{N, i} \right) -  h\left(L_i \right)  \right)^2\right] \nonumber \\
    & = \mathbb{E} \left[ \left( \frac{1}{M} \sum_{i=1}^M h'\left( L_i \right) \left( \hat{L}_{N, i} - L_i \right) +  \frac{1}{2M} \sum_{i=1}^M h''\left( z_i \right) \left( \hat{L}_{N, i} - L_i \right)^2 \right)^2\right] \nonumber \\
    & \leq 2 \underbrace{\mathbb{E} \left[ \left( \frac{1}{M} \sum_{i=1}^M h'\left( L_i \right) \left( \hat{L}_{N, i}- L_i \right) \right)^2\right]}_{S_1} \nonumber \\
    & ~~~~ + 2 \underbrace{\mathbb{E} \left[ \left( \frac{1}{2M} \sum_{i=1}^M h''\left( z_i \right) \left( \hat{L}_{N, i} - L_i \right)^2 \right)^2\right]}_{S_2},
\end{align}
where \textcolor{red}{$z_i$ is between $L_i$ and $\hat{L}_{N,i}$, and} the last inequality is due to $2ab \leq a^2 + b^2$ for any $a, b \in \mathbb{R}$. 
The two terms on the right-hand side of Equation~\eqref{eq1:taylor-sns} are analyzed separately.
We start with the first term $S_1$.

@@

\begin{align}\label{eq1:bias-sns-smooth}
    \text{Bias}(\hat{\rho}_{M, N})
    & = \mathbb{E} \left[ \hat{\rho}_{M, N} \right] - \rho \nonumber \\
    & = \mathbb{E} \left[ \frac{1}{M} \sum_{i=1}^M h\left( \hat{L}_{N, i} \right) \right] - \mathbb{E} \left[ h\left(L \right) \right]  \nonumber \\
    & = \mathbb{E} \left[ h\left( \hat{L}_N \right) - h\left( L \right) \right] \nonumber \\
    & = \mathbb{E} \left[h'\left( L \right) \left( \hat{L}_N - L \right) + \frac{1}{2} h''\left( z \right) \left( \hat{L}_N - L \right)^2 \right],
\end{align}
where \textcolor{red}{$z_i$ is between $L_i$ and $\hat{L}_{N,i}$, and} the last equality follows from the Taylor expansion of the smooth function $h$.
The first and second order Taylor expansion terms are analyzed separately in Equation~\eqref{eq1:bias-sns-smooth-Taylor1} and Equation~\eqref{eq1:bias-sns-smooth-Taylor2}.

@@

The proof techniques used in deriving Theorem~\ref{thm1:sns-smooth} is completely different from the one used in~\cite{gordy2010nested}.
The analysis in~\cite{gordy2010nested} is based on the differentiablity of the joint density of $Y$ and the average inner simulation noise, which is difficult to verify in practice.
Instead, we use a Taylor expansion of the smooth function $h$ to analyze the convergence of the standard nested simulation procedure.
The critical assumption in our derivation is Assumption~\ref{as1:sns-noise-var}, which is necessary to ensure the existence of the fourth moment of the simulation noise and the convergence of $S_2$, the second order term in the Taylor expansion.
Assumption~\ref{as1:sns-noise-var} is a moment condition that is easier to verify in practice than conditions on the joint density.
\textcolor{red}{\sout{As stated in Theorem, the convergence in \gls{mse} automatically implies the convergence in probabilistic order.}}

% \begin{corollary}
%     Let $h$ be a smooth function. 
%     The AE of the standard nested simulation procedure converges in probabilistic order $\Gamma^{-1/3}$, that is,
%     $$\left| \hat{\rho}_{M, N} - \rho \right| = \mathcal{O}_\mathbb{P}(\Gamma^{-1/3}).$$
% \end{corollary}

@@

\textcolor{red}{\sout{Immediately from Theorem, the convergence in \gls{mse} automatically implies the convergence in probabilistic order.}}

% \begin{corollary}
%     Let $h$ be a Lipschitz continuous function. AE of the standard nested simulation procedure converges in probabilistic order $\Gamma^{-1/3}$, that is,
%     $$\left| \hat{\rho}_{M, N} - \rho \right| = \mathcal{O}_\mathbb{P}(\Gamma^{-1/4}).$$
% \end{corollary}

@@

Assumption~\ref{as1:krr-domain} rules out the possibility of the outer scenario $X$ being a normal random variable, which is a common assumption in the literature.
Furthermore, the convergence analysis of the \gls{krr}-based nested simulation procedure is shown in terms of \gls{ae} rather than in \gls{mse}, which is due to the \textcolor{red}{analytical properties} of the KRR metatmodel.

\section{Finite-Sample Experiments}\label{sec1:numerical-experiments}
The theoretical framework has lent itself for a comparison of the asymptotic convergence behavior for different nested simulation procedures.
However, a simulation budget in practice is almost always finite.
In this section, we conduct a series of numerical experiments to compare the empirical convergence of the nested simulation procedures for different risk measures, option types, and asset dimensions.
Numerical experiments are conducted on portfolios that consist of options on $d$ underlying assets, whose dynamics follow a multidimensional geometric Brownian motion with $0.3$ pairwise correlation.
\textcolor{red}{The initial values of the assets are set to be $100$.}
\textcolor{red}{The drifts are set to be $0.08$, and the risk free rate is set to be $0.05$.}

@@

The procedures are compared for 5 types of risk measures:
\begin{itemize}
    \item a quadratic tracking error,
    \item a mean excess loss over a threshold $u$,
    \item a probability of a large loss over a threshold $u$,
    \item the \gls{var}, and
    \item the \gls{cvar},
\end{itemize}
where the threshold $u$ for the mean excess loss and the probability of a large loss is set to be 90\% \gls{var}.
The procedures are compared for different portfolios consisting of different types of options:
\begin{itemize}
    \item   Portfolio 1 consists of $d$ assets.
    This portfolio contains 3 European call options written on each asset with strikes $90$, $100$, and $110$, respectively. 
    \item   Portfolio 2 consists of $d$ assets.
    This portfolio contains 3 geometric Asian options written on each asset with strikes $90$, $100$, and $110$, respectively. 
    \item   Portfolio 3 consists of $d$ assets.
    This portfolio contains 3 up-and-out barrier call options written on each asset with strikes $90$, $100$, and $110$, respectively. They have a barrier level of $120$.
    \item   Portfolio 4 considers $d$ assets.
    This portfolio contains 3 down-and-out barrier call options written on each asset with strikes $90$, $100$, and $110$, respectively. They have a barrier level of $90$.
    \item   Portfolio 5 contains 1 asset.
    This portfolio longs 2 down-and-out barrier put options and shorts 1 barrier down-and-out put option. 
\end{itemize}
Except for Portfolio 5, 5 different asset dimensions are considered, i.e., $d = 1, 2, 5, 10, 20$.
\textcolor{red}{All options have a maturity of $1$ year, and we are interested in the value of the portfolio at time $3/50$ year from now.}
525 experiment settings that arise from an exhaustive combination of the above simulation procedures, risk measures, portfolios, and asset dimensions are generated.
For each experiment setting, the estimation of the risk measure is repeated \num{1000} times to obtain the empirical \gls{mse} of the corresponding estimator under a range of simulation budgets.
The total simulation budget $\Gamma$ ranges from $\num{10000}$ to $\num{10240000}$ in a geometric progression with a common ratio of $2$.
The empirical convergence results of each estimator are measured and recorded to illustrate their empirical behavior under different risk measures, option types, and asset dimensions.
\textcolor{red}{All numerical experiments are conducted on a linux server with four Intel Xeon Gold 6230 20-core 2.1 GHz CPU with 768 GB RAM.}

@@

The left part of Figure \ref{fig1:reg_lb} contains the \gls{mse}s of the regression procedure for budget sizes that are smaller than $10^3$. 
Slopes of the fitted lines on the left correspond to the empirical rate of convergence of the regression procedure for budget levels between $10^3$ and $10^4$.
To investigate the convergence behavior for higher budget levels, we conduct additional experiments for the European call option with a dimension of $20$. 
The additional experiments are summarized on the right side of Figure \ref{fig1:reg_lb}.
After reaching a certain budget level, i.e., $\Gamma = 10^6$ in our case, the empirical rate of convergence for the regression-based nested simulation procedure approaches its asymptotic rate. 
For nested simulation procedures with a biased metamodel, the metamodel estimates of the true inner simulation are poor, especially for smaller budget sizes. 
We are able to clearly observe this phenomenon for the regression metamodel, and it can be explained by dividing the \gls{mse} into metamodeling bias and simulation variance.
\begin{itemize}
    \item For small budget sizes, the improvement in the bias of the regression metamodel dominates the improvement in the simulation variance. 
    Performing poorly for extremely low simulation budgets, the regression metamodel improves dramatically as the simulation budget increases.
    \item As the simulation budget gets higher, the improvement of the regression bias becomes negligible compared with that of the simulation variance. 
    The regression metamodel ceases to improve after reaching a certain level ($\Gamma = 10^6$ in our case), and the improvement of simulation variance dominates.
\end{itemize}
Due to high computational costs, we are not able to conduct experiments for higher budget levels, but we expect the \gls{mse} of the regression-based nested simulation procedure to stabilize after $\Gamma = 10^6$, and the empirical rate of convergence to approach its asymptotic rate.
\textcolor{red}{The empirical convergence rates reported in the graph legends are higher than the actual rates after regression-based nested simulation procedure reaches the asymptotic convergence regime.}
In the context of nested simulation procedures, a parametric regression metamodel has several advantages over a non-parametric regression metamodel.
\begin{itemize}
    \item Parametric regression achieves a good empirical convergence behavior for a moderate simulation budget.
    \item Parametric regression is insensitive to changes in the asset dimension.
    \item Parametric regression is easier to implement.
    It does not require cross-validation to select the hyperparameters of the metamodel.
\end{itemize}
However, parametric regression suffers from the model misspecification risk.
More specifically, selecting a wrong regression basis can lead to a poor metamodel estimate, where the \gls{mse} of the nested simulation procedure is dominated by the model error of the metamodel~\citep{broadie2015risk}.

@@

Our previous numerical experiments have been conducted under the assumption that the underlying asset dynamics follow a multidimensional geometric Brownian motion with $0.3$ pairwise correlation.
To examine the sensitivity of the empirical convergence behavior to the asset model, we consider a stochastic volatility model of a Heston type~\citep{heston1993closed}.
\textcolor{red}{In a Heston model, the asset price and the volatility are correlated, and the volatility is a stochastic process.}

@@

\textcolor{red}{In this experiment, the initial asset price and the volatility are set to be $100$ and $0.2$, respectively. The parameters are set to be $\mu = 0.08$, $\kappa = 2$, $\theta = 0.04$, $\xi = 0.1$.}

@@

The \gls{mlmc} procedure is a variance reduction technique that is designed to reduce the computational cost of nested simulation procedures.
The theoretical analysis in~\cite{giles2019multilevel} shows that the \gls{mlmc} procedure has a faster empirical rate of convergence than the standard nested simulation procedure when the risk measure of interest is the probability of a large loss over a threshold $u$, i.e., the nested expectation case with $h$ being an indicator function.
\textcolor{red}{In this numerical experiment, the initial number of inner replications, the refinement factor, the r-value for adaptive algorithm are set to be $4$, $4$, and $1.5$, respectively.}
\textcolor{red}{We note that the \gls{mlmc} procedure focuses on adaptive allocation of the simulation budget and is fundamentally different from supervised learning-based nested simulation procedures. And their results are not directly comparable.}

>>>>

This paper presents a survey study of some popular nested simulation procedures that have both asymptotic convergence analysis and finite-sample performance evaluation.
Many procedures have been proposed in the literature, but they are not directly comparable because they use different assumptions and different numerical examples in their studies.
Within a common analytical framework, we first summarize and compare the asymptotic convergence rates of these procedures.
Their asymptotic convergence results are closely examined for their assumptions that guarantee the convergence.

@@

The regression-based nested simulation procedure has the least stringent smoothness assumption.
In general, a more complex metamodel requires a higher-order smoothness for $h$ for its convergence analysis.
Despite being more advanced than kernel smoothing, the \gls{krr}-based procedure requires a less stringent smoothness assumption on $h$.
At first sight, it is counterintuitive that a more complex metamodel requires a less stringent smoothness assumption.
This phenomenon is due to the fact that the convergence analysis for the \gls{krr}-based nested simulation procedure is shown in terms of \gls{ae}, a different error metric than \gls{mse}.
In the appendix, Section~\ref{appendix:connection-mse-absolute-error} includes a discussion of the connection between the \gls{mse} and the \gls{ae} of the estimator in the context of nested simulation procedures.
In Table~\ref{tab1:smoothness}, the standard nested simulation procedure is the only procedure without an asymptotic convergence analysis for smooth $h$.
Section~\ref{sec1:sns} fills this gap by providing the asymptotic convergence analysis for the standard nested simulation procedure in terms of \gls{mse}.

@@

The \gls{mlmc} method is a variance reduction technique that uses a hierarchy of approximations to the quantity of interest, and it uses the difference between the approximations to reduce the variance of the estimator.
The \gls{mlmc} method is particularly useful when the quantity of interest is expensive to evaluate, and the standard \gls{mc} estimator has a high variance.
For the nested expectation form $\rho = \mathbb{E}[h(L)]$, the \gls{mlmc} method selects an approximation level $L$ with sufficient accuracy, and it uses the difference between the approximations to reduce the variance of the estimator.

@@

\begin{itemize}
    \item   Regression:
            \begin{equation*}
            \hat{L}^{\text{REG}}_{M, N}(X) = \Phi(X) \hat{\beta},
            \end{equation*}
            where $\Phi$ is a chosen basis, and $\hat{\beta}$ is estimated from the training samples.
            In~\cite{broadie2015risk}, the convergence analysis is performed on the expectation (Equation~\eqref{eq1:sl-E}) and for smooth and Lipschitz continuous $h$. 
    \item   Kernel smoothing:
            $$\hat{L}^{\text{KS}}_{M, N}(X) = \frac{\sum_{i=1}^M \hat{L}_{N, i} K_w(X - X_i)}{\sum_{i=1}^M K_w(X - X_i)}, $$
            where $K_w$ is a kernel function with bandwidth $w$.
            ~\cite{nadaraya1964estimating} and ~\cite{watson1964smooth} originally proposed this kernel smoothing method for a non-parametric regression, and it is widely known in the literature as a Nadaraya-Watson kernel regression.
            ~\cite{hong2017kernel} provides convergence analysis for metamodel predictions of the training samples (Equation~\eqref{eq1:sl-train}), and the convergence analysis is provided for smooth, hockey-stick, and indicator $h$.

@@

Theoretical properties of different metamodels lead to different convergence results.
More specifically, the \gls{krr}-based nested simulation~\citep{wang2022smooth} provides a convergence analysis in terms of \gls{ae}.
\begin{align}\label{eq1:ae}
    & \min_{M, N}  & \text{AE}(\hat{\rho}^{\text{SL}}_{M, N}) = \mathbb{E} \left[ \left| \hat{\rho}^{\text{KRR}}_{M, N} - \rho \right| \right] \nonumber \\
    & \text{subject to} & M \cdot N = \Gamma
\end{align}
Section~\ref{appendix:connection-mse-absolute-error} draws the connection between the \gls{mse} and the \gls{ae} of the estimator in the context of nested simulation procedures.

@@

\section{Asymptotic Analysis}\label{sec1:asymptotic-convergence}
In the first part of this section, we summarize the existing asymptotic convergence results of the nested simulation procedures in the literature, and we compare their critical assumptions that guarantee the convergence.
The remainder of this section aims to fill the gap in the literature by offering the following steps:
\begin{itemize}
    \item provide the asymptotic convergence results for the standard nested simulation procedure, and
    \item illustrate the asymptotic rate of convergence of a \gls{knn}-based nested simulation procedure.
\end{itemize}

@@

In~\cite{wang2022smooth}, the authors of the \gls{krr}-based nested simulation procedures claim to have bridged the gap between the cubic and square root convergence rates of nested simulation procedures. However, they analyze convergence in probabilistic order, and it is only applicable in terms of \gls{ae}. 
In Section~\ref{appendix:connection-mse-absolute-error}, we illustrate the connection between the convergence in \gls{mse} and the convergence in \gls{ae}.

@@

In Equation~\eqref{eq1:mse-sns}, the first inequality follows from Cauchy-Schwarz inequality.
One way to express the Cauchy-Schwarz inequality is 
$(x_1y_1 + x_2y_2)^2 \leq (x_1^2 + x_2^2)(y_1^2 + y_2^2)$.
Let $\mathbf{x} = (x_1, x_2)$ and $\mathbf{y} = (y_1, y_2)$.
The Cauchy-Schwarz inequality can be written as
\begin{equation*}
    \langle \mathbf{x}, \mathbf{y} \rangle^2  = \left( \Vert \mathbf{x} \Vert \cdot \Vert \mathbf{y} \Vert \cdot \cos a \right)^2 \leq \Vert \mathbf{x} \Vert^2 \cdot \Vert \mathbf{y} \Vert^2.
\end{equation*}
By setting $x_1 = \rho_{M,N}- \rho_M$, $x_2 = \rho_M - \rho$, $y_1 = y_2 = 1$, we have 
\begin{align*}
    \left( \rho_{M,N} - \rho_M + \rho_M - \rho \right)^2 
    & \leq \left( (\rho_{M,N} - \rho_M)^2 + (\rho_M - \rho)^2 \right) \left( 1^2 + 1^2 \right) \\
    & = 2 \left( (\rho_{M,N} - \rho_M)^2 + (\rho_M - \rho)^2 \right) \\
    & = 2  (\rho_{M,N} - \rho_M)^2 + 2 (\rho_M - \rho)^2.
\end{align*}
The last equality follows from Assumption~\ref{as1:sns}.
The analysis of the first term is different for smooth and Lipschitz continuous $h$. 
We will analyze them separately below.

@@

\begin{align}\label{eq1:taylor-sns}
    & \mathbb{E} \left[  \left( \frac{1}{M} \sum_{i=1}^M h\left( \hat{L}_{N, i} \right) -  h\left(L_i \right)  \right)^2\right] \nonumber \\
    & = \mathbb{E} \left[ \left( \frac{1}{M} \sum_{i=1}^M h'\left( L_i \right) \left( \hat{L}_{N, i} - L_i \right) +  \frac{1}{2M} \sum_{i=1}^M h''\left( z_i \right) \left( \hat{L}_{N, i} - L_i \right)^2 \right)^2\right] \nonumber \\
    & \leq 2 \underbrace{\mathbb{E} \left[ \left( \frac{1}{M} \sum_{i=1}^M h'\left( L_i \right) \left( \hat{L}_{N, i}- L_i \right) \right)^2\right]}_{S_1} \nonumber \\
    & ~~~~ + 2 \underbrace{\mathbb{E} \left[ \left( \frac{1}{2M} \sum_{i=1}^M h''\left( z_i \right) \left( \hat{L}_{N, i} - L_i \right)^2 \right)^2\right]}_{S_2},
\end{align}
where $z_i$ is between $L_i$ and $\hat{L}_{N,i}$, and the last inequality is due to $2ab \leq a^2 + b^2$ for any $a, b \in \mathbb{R}$. 
The two terms on the right-hand side of Equation~\eqref{eq1:taylor-sns} are analyzed separately.
We start with the first term $S_1$.

@@

\begin{align}\label{eq1:bias-sns-smooth}
    \text{Bias}(\hat{\rho}_{M, N})
    & = \mathbb{E} \left[ \hat{\rho}_{M, N} \right] - \rho \nonumber \\
    & = \mathbb{E} \left[ \frac{1}{M} \sum_{i=1}^M h\left( \hat{L}_{N, i} \right) \right] - \mathbb{E} \left[ h\left(L \right) \right]  \nonumber \\
    & = \mathbb{E} \left[ h\left( \hat{L}_N \right) - h\left( L \right) \right] \nonumber \\
    & = \mathbb{E} \left[h'\left( L \right) \left( \hat{L}_N - L \right) + \frac{1}{2} h''\left( z \right) \left( \hat{L}_N - L \right)^2 \right],
\end{align}
where $z_i$ is between $L_i$ and $\hat{L}_{N,i}$, and the last equality follows from the Taylor expansion of the smooth function $h$.
The first and second order Taylor expansion terms are analyzed separately in Equation~\eqref{eq1:bias-sns-smooth-Taylor1} and Equation~\eqref{eq1:bias-sns-smooth-Taylor2}.

@@

The proof techniques used in deriving Theorem~\ref{thm1:sns-smooth} is completely different from the one used in~\cite{gordy2010nested}.
The analysis in~\cite{gordy2010nested} is based on the differentiablity of the joint density of $Y$ and the average inner simulation noise, which is difficult to verify in practice.
Instead, we use a Taylor expansion of the smooth function $h$ to analyze the convergence of the standard nested simulation procedure.
The critical assumption in our derivation is Assumption~\ref{as1:sns-noise-var}, which is necessary to ensure the existence of the fourth moment of the simulation noise and the convergence of $S_2$, the second order term in the Taylor expansion.
Assumption~\ref{as1:sns-noise-var} is a moment condition that is easier to verify in practice than conditions on the joint density.

@@

@@

Assumption~\ref{as1:krr-domain} rules out the possibility of the outer scenario $X$ being a normal random variable, which is a common assumption in the literature.
Furthermore, the convergence analysis of the \gls{krr}-based nested simulation procedure is shown in terms of \gls{ae} rather than in \gls{mse}, which is due to the analytical properties of the \gls{krr} metatmodel.

\section{Finite-Sample Experiments}\label{sec1:numerical-experiments}
The theoretical framework has lent itself for a comparison of the asymptotic convergence behavior for different nested simulation procedures.
However, a simulation budget in practice is almost always finite.
In this section, we conduct a series of numerical experiments to compare the empirical convergence of the nested simulation procedures for different risk measures, option types, and asset dimensions.
Numerical experiments are conducted on portfolios that consist of options on $d$ underlying assets, whose dynamics follow a multidimensional geometric Brownian motion with $0.3$ pairwise correlation.
The initial values of the assets are set to be $100$.
The drifts are set to be $0.08$, and the risk free rate is set to be $0.05$.

@@

The procedures are compared for 5 types of risk measures:
\begin{itemize}
    \item a quadratic tracking error,
    \item a mean excess loss over a threshold $u$,
    \item a probability of a large loss over a threshold $u$,
    \item the \gls{var}, and
    \item the \gls{cvar},
\end{itemize}
where the threshold $u$ for the mean excess loss and the probability of a large loss is set to be 90\% \gls{var}.
The procedures are compared for different portfolios consisting of different types of options:
\begin{itemize}
    \item   Portfolio 1 consists of $d$ assets.
    This portfolio contains 3 European call options written on each asset with strikes $90$, $100$, and $110$, respectively. 
    \item   Portfolio 2 consists of $d$ assets.
    This portfolio contains 3 geometric Asian options written on each asset with strikes $90$, $100$, and $110$, respectively. 
    \item   Portfolio 3 consists of $d$ assets.
    This portfolio contains 3 up-and-out barrier call options written on each asset with strikes $90$, $100$, and $110$, respectively. They have a barrier level of $120$.
    \item   Portfolio 4 considers $d$ assets.
    This portfolio contains 3 down-and-out barrier call options written on each asset with strikes $90$, $100$, and $110$, respectively. They have a barrier level of $90$.
    \item   Portfolio 5 contains 1 asset.
    This portfolio longs 2 down-and-out barrier put options and shorts 1 barrier down-and-out put option. 
\end{itemize}
Except for Portfolio 5, 5 different asset dimensions are considered, i.e., $d = 1, 2, 5, 10, 20$.
All options have a maturity of $1$ year, and we are interested in the value of the portfolio at time $3/50$ year from now.
525 experiment settings that arise from an exhaustive combination of the above simulation procedures, risk measures, portfolios, and asset dimensions are generated.
For each experiment setting, the estimation of the risk measure is repeated \num{1000} times to obtain the empirical \gls{mse} of the corresponding estimator under a range of simulation budgets.
The total simulation budget $\Gamma$ ranges from $\num{10000}$ to $\num{10240000}$ in a geometric progression with a common ratio of $2$.
The empirical convergence results of each estimator are measured and recorded to illustrate their empirical behavior under different risk measures, option types, and asset dimensions.
All numerical experiments are conducted on a linux server with four Intel Xeon Gold 6230 20-core 2.1 GHz CPU with 768 GB RAM.

@@

The left part of Figure \ref{fig1:reg_lb} contains the \gls{mse}s of the regression procedure for budget sizes that are smaller than $10^3$. 
Slopes of the fitted lines on the left correspond to the empirical rate of convergence of the regression procedure for budget levels between $10^3$ and $10^4$.
To investigate the convergence behavior for higher budget levels, we conduct additional experiments for the European call option with a dimension of $20$. 
The additional experiments are summarized on the right side of Figure \ref{fig1:reg_lb}.
After reaching a certain budget level, i.e., $\Gamma = 10^6$ in our case, the empirical rate of convergence for the regression-based nested simulation procedure approaches its asymptotic rate. 
For nested simulation procedures with a biased metamodel, the metamodel estimates of the true inner simulation are poor, especially for smaller budget sizes. 
We are able to clearly observe this phenomenon for the regression metamodel, and it can be explained by dividing the \gls{mse} into metamodeling bias and simulation variance.
\begin{itemize}
    \item For small budget sizes, the improvement in the bias of the regression metamodel dominates the improvement in the simulation variance. 
    Performing poorly for extremely low simulation budgets, the regression metamodel improves dramatically as the simulation budget increases.
    \item As the simulation budget gets higher, the improvement of the regression bias becomes negligible compared with that of the simulation variance. 
    The regression metamodel ceases to improve after reaching a certain level ($\Gamma = 10^6$ in our case), and the improvement of simulation variance dominates.
\end{itemize}
Due to high computational costs, we are not able to conduct experiments for higher budget levels, but we expect the \gls{mse} of the regression-based nested simulation procedure to stabilize after $\Gamma = 10^6$, and the empirical rate of convergence to approach its asymptotic rate.
The empirical convergence rates reported in the graph legends are higher than the actual rates after regression-based nested simulation procedure reaches the asymptotic convergence regime.
In the context of nested simulation procedures, a parametric regression metamodel has several advantages over a non-parametric regression metamodel.
\begin{itemize}
    \item Parametric regression achieves a good empirical convergence behavior for a moderate simulation budget.
    \item Parametric regression is insensitive to changes in the asset dimension.
    \item Parametric regression is easier to implement.
    It does not require cross-validation to select the hyperparameters of the metamodel.
\end{itemize}
However, parametric regression suffers from the model misspecification risk.
More specifically, selecting a wrong regression basis can lead to a poor metamodel estimate, where the \gls{mse} of the nested simulation procedure is dominated by the model error of the metamodel~\citep{broadie2015risk}.

@@

Our previous numerical experiments have been conducted under the assumption that the underlying asset dynamics follow a multidimensional geometric Brownian motion with $0.3$ pairwise correlation.
To examine the sensitivity of the empirical convergence behavior to the asset model, we consider a stochastic volatility model of a Heston type~\citep{heston1993closed}.
In a Heston model, the asset price and the volatility are correlated, and the volatility is a stochastic process.

@@

In this experiment, the initial asset price and the volatility are set to be $100$ and $0.2$, respectively. The parameters are set to be $\mu = 0.08$, $\kappa = 2$, $\theta = 0.04$, $\xi = 0.1$.

@@

The \gls{mlmc} procedure is a variance reduction technique that is designed to reduce the computational cost of nested simulation procedures.
The theoretical analysis in~\cite{giles2019multilevel} shows that the \gls{mlmc} procedure has a faster empirical rate of convergence than the standard nested simulation procedure when the risk measure of interest is the probability of a large loss over a threshold $u$, i.e., the nested expectation case with $h$ being an indicator function.
In this numerical experiment, the initial number of inner replications, the refinement factor, the r-value for adaptive algorithm are set to be $4$, $4$, and $1.5$, respectively.
We note that the \gls{mlmc} procedure focuses on adaptive allocation of the simulation budget and is fundamentally different from supervised learning-based nested simulation procedures. And their results are not directly comparable.
